%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Employment}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior/Leader Frontend Software Engineer} % Job title
    {Shanghai Fumasoft Co,.Ltd} % Organization
    {Shanghai, China} % Location
    {December 2020 -- now} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Created js bridge for hybrid app enabling both sending and receiving of messages each other so that solved issues caused by network and latency and improved the UX. }
        \item{Charged and fixed various issues of company main product, and collaborated with team members using version control systems such as Git to organize modifications and assign tasks.}
        \item{Mannaged 1 FE engineer, 1 iOS engineer and 1 Android engineer; led and designed the method for every sprint and requirement.}
        \item{Built CMS website by using velocity template, creating gulp task to compile velocity template automatically to save lots of time to debug.}
      \end{cvitems}
    }
  
%---------------------------------------------------------

  \cventry
    {Frontend Software Engineer} % Job title
    {The State Grid Corporation - Shineenergy } % Organization
    {Shanghai, China} % Location
    {August 2020 -- November 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Built multi pages print module for grid maps and info window for grid node and devices.}
        \item{Coordinated with windows client developers to design the SSO login module(same origin)}
        \item{Built style configuration page for users to customize their preference.}
        \item{Reported work and plans every morning on stand-up meeting}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Publicis Groupe - Publicissapient} % Organization
    {Shanghai, China} % Location
    {April 2019 -- August 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Worked on the UIs of various Minisites for Huawei events and meetings like MBBF, HDC, etc.}
        \item{Built creative and effective official websites for Marriott, DS auto and SAIC motor.}
        \item{Collaborated with team members from 3 time zones (Singapore, Japan, India) and produced EDMs made on time for 3 weeks.}
        \item{Managed SWE interns for 2 months; led the launches and frameworks of their projects; received outstanding feedback on my leadership and problem-solving.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
