%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Employment \emoji{briefcase}}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior/Leader Frontend Software Engineer} % Job title
    {\emoji{office-building} Shanghai Fumasoft Co,.Ltd} % Organization
    {Shanghai, China} % Location
    {December 2020 -- now} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Created js bridge for hybrid app enable both to send and receive messages each other so that solved issues caused by network and latency and improved the UX. }
        \item{Charged and fixed various issues of company main product, and collaborated with team members using version control systems such as Git to organize modifications and assign tasks.}
        \item{Mannaged 1 engineer, 1 iOS engineer and 1 Android engineer; led and design the method for every sprint and requirement.}
        \item{Build CMS website by using velocity template, create gulp task to compile velocity template automatically to save lots of time to debug.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {\emoji{office-building}Publicis Groupe - Publicissapient} % Organization
    {Shanghai, China} % Location
    {April 2019 -- August 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Worked on the UIs of various Minisites for Huawei events and meetings like MBBF, HDC, etc.}
        \item{Built creative and effective official websites for Marriott, DS auto and SAIC motor.}
        \item{Collaborated with team members from 3 time zones (Singapore, Japan, India) and produced EDMs made on time for 3 weeks.}
        \item{Mannaged SWE interns for 2 months; led the launches and framworks of their projects; received outstanding feedback on my leadership and problem-resolving.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
