%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Recent Advanced Projects \emoji{brick}}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Shanghai Fumasoft Co,.Ltd} % Organization
    {Fumamx hybrid App} % Project
    {Shanghai, China} % Location
    {January 2021} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Migrated React Native App to hybrid App so that users can get better experience and use more native functionalities.}
        \item {Applied listeners on Vue router to receive message from native App and wrapped postMessage api for sending message to native App.}
        \item {Managed 1 iOS engineer and 1 Android engineer, tracked their progresses and raised meeting for better collaboration .}
      \end{cvitems}
    }

%---------------------------------------------------------

    \cventry
    {Shanghai Fumasoft Co,.Ltd} % Organization
    {CMS website template (PC \& Mobile)} % Project
    {Shanghai, China} % Location
    {March 2021} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {According to the requirement, built a new framework with handlebar.js, tailwind.css and gulp.js. }
        \item {Looked into velocity template, and imported gulp-velocity plugin into gulp pipeline so that automatically generate velocity file.}
        \item {Made development Plan to teammate by using Gantt chart so that the progress looks clearer.}
      \end{cvitems}
    }

    \cventry
    {Publicis Groupe - Publicissapient} % Organization
    {IQOS EDM Email template} % Project
    {Shanghai, China} % Location
    {April 2020} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Collaborated with team from 3 time zones, reported my work on meeting and discussed to backend for better implementing on CMS.}
        \item {Built responsive design by media query, used gulp.js to automatically upload files and used Litums to debug email for each platform.}
        \item {Joined the mjml official stack group, directly ask the solutions and suggestions then quickly resolved.}
      \end{cvitems}
    }
    

%---------------------------------------------------------
\end{cventries}
